ПАРАЛЛЕЛЬНЫЙ АЛГОРИТМ ДЛЯ ПОЛУЧЕНИЯ РАВНОМЕРНОГО ПРИБЛИЖЕНИЯ РЕШЕНИЙ МНОЖЕСТВА ЗАДАЧ ГЛОБАЛЬНОЙ ОПТИМИЗАЦИИ С НЕЛИНЕЙНЫМИ ОГРАНИЧЕНИЯМИ \footnote{Статья рекомендована к публикации программным комитетом Международной научной конференции <<Параллельные вычислительные технологии (ПаВТ) 2020>>.}

### 2020-02-27 2020/PAVT_Sovrasov/vm_journal/vm_paper.tex
PAVT: Final fixes to the journal version

\classify{УДК 123.456, 789.012}

@@

\received{Поступила в редакцию: 26.02.2020}

@@

\received{Received: 26.02.2020}

@@

\bibitem{BarkalovLebedev2017}
Barkalov K., Lebedev I.
\newblock Comparing two approaches for solving constrained global optimization
  problems
\newblock // Learning and Intelligent Optimization. Springer International
  Publishing, Cham. 2017. P. 301--306.
\newblock \doi{10.1007/978-3-319-69404-7_22}

@@

@@

\bibitem{Paulavicius2011}
{Paulavivcius R., Zilinskas J., Grothey A.}
\newblock Parallel branch and bound for global optimization with combination of
  lipschitz bounds //
\newblock Optim. Method. Softw. 1997. Vol. 26, No. 3. P. 487--498.
\newblock \doi{10.1080/10556788.2010.551537}

@@

\bibitem{grishaginClass}
{Grishagin V.}
\newblock {Operating characteristics of some global search algorithms}
\newblock // Problems of Stochastic Search. Zinatne, Riga. 1978. (in Russian)

\bibitem{Norkin1992}
{Norkin V. I.}
\newblock Towards Pijavskyj's method for solving common global optimization problem //
\newblock J. Comput. Math. Math. Phys. 1992. Vol. 32, no. 7. P. 992--1006. (in Russian)

>>>>

\classify{УДК 004.021, 519.6}

@@

\received{Поступила в редакцию: 27.02.2020}

@@

\received{Received: 27.02.2020}

@@

\bibitem{BarkalovLebedev2017}
Barkalov K., Lebedev I.
\newblock Comparing two approaches for solving constrained global optimization
  problems.
\newblock Learning and Intelligent Optimization. Springer International
  Publishing, Cham. 2017. P. 301--306.
\newblock \doi{10.1007/978-3-319-69404-7_22}

\bibitem{BarkalovLebedev2017_2}
Barkalov K., Lebedev I.
\newblock Parallel algorithm for solving constrained global optimization
  problems.
\newblock Parallel Computing Technologies. Springer International
  Publishing, Cham. 2017. P. 396--404.
\newblock \doi{10.1007/978-3-319-62932-2_38}

\bibitem{BarkalovStrongin2018}
Barkalov K., Strongin R.
\newblock Solving a set of global optimization problems by the parallel
  technique with uniform convergence.
\newblock J. of Global Optimization. 2018. Vol. 71, No. 1. P. 21--36.
\newblock \doi{10.1007/s10898-017-0555-4}

\bibitem{Beiranvand2017}
Beiranvand V., Hare W., Lucet Y.
\newblock Best practices for comparing optimization algorithms.
\newblock Optimization and Engineering. 2017. Vol. 18, No. 4. P. 815--848.
\newblock \doi{10.1007/s11081-017-9366-1}

@@

\bibitem{Evtushenko2013}
Evtushenko Y., Posypkin M.
\newblock A deterministic approach to global box-constrained optimization.
\newblock Optim. Lett. 2013. Vol. 7 P. 819--829.
\newblock \doi{10.1007/s11590-012-0452-1}

\bibitem{Gaviano2003}
{Gaviano M., Kvasov D.E., Lera D., Sergeev Ya.D.}
\newblock Software for generation of classes of test functions with known local
  and global minima for global optimization.
\newblock ACM Transactions on Mathematical Software. 2003. Vol. 29, No. 4. P.
  469--480.
\newblock \doi{10.1145/962437.962444}

@@

\bibitem{Jones2009}
{Jones D.R.}
\newblock The direct global optimization algorithm.
\newblock The Encyclopedia of Optimization. Springer, Heidelberg. 2009. P.
  725--735.
\newblock \doi{10.1007/978-0-387-74759-0_128}

\bibitem{Paulavicius2011}
{Paulavivcius R., Zilinskas J., Grothey A.}
\newblock Parallel branch and bound for global optimization with combination of
  lipschitz bounds.
\newblock Optim. Method. Softw. 1997. Vol. 26, No. 3. P. 487--498.
\newblock \doi{10.1080/10556788.2010.551537}

\bibitem{RiquelmeLucken2015}
{Riquelme} N., {Von Lucken} C., {Baran} B.
\newblock Performance metrics in multi-objective optimization.
\newblock2015 Latin American Computing Conference (CLEI). 2015. P. 1--11.
\newblock \doi{10.1109/clei.2015.7360024}

@@

\bibitem{grishaginClass}
{Grishagin V.}
\newblock {Operating characteristics of some global search algorithms.}
\newblock Problems of Stochastic Search. Zinatne, Riga. 1978. (in Russian)

\bibitem{Norkin1992}
{Norkin V. I.}
\newblock Towards Pijavskyj's method for solving common global optimization problem.
\newblock J. Comput. Math. Math. Phys. 1992. Vol. 32, no. 7. P. 992--1006. (in Russian)
